### 2019-03-04 report/final-report.tex
caption

\begin{figure}
  \centering
  \includegraphics{figs/examples.eps}
  \caption{Average number of random examples required to synthesize benchmark
    programs.  {\bf Examples Required} is the average number of randomly
    generated examples needed to correctly synthesize the lens.  {\bf
      Determinize Permutations} is the theoretical number of examples required
    to determinize the choice all the permutations in \RigidSynth{}.
    In practice, far fewer examples are
    needed to synthesize the correct lens than would be predicted by the number
    required to determinize permutations.}
  \label{fig:exs-reqd}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{figs/examples.eps}
  \caption{Average number of random examples required to synthesize benchmark
    programs. %  {\bf Examples Required} is the average number of randomly
    % generated examples needed to correctly synthesize the lens.
    % {\bf
    %   Determinize Permutations} is the theoretical number of examples required
    % to determinize the choice all the permutations in \RigidSynth{}.
    % In practice, far fewer examples are
    % needed to synthesize the correct lens than would be predicted by the number
    % required to determinize permutations.
  }
  \label{fig:exs-reqd}
\end{figure}
